---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  fig.align="center"
)
```

[![deprecated](http://badges.github.io/stability-badges/dist/deprecated.svg)](http://github.com/badges/stability-badges)

# rjd3x13 (Old Repository) [DEPRECATED]

**Important:** This repository is now deprecated and no longer
maintained. Please refer to the [new
repository](https://github.com/rjdemetra/rjd3x13) for the latest
developments, issues, and pull requests.

## New Repository

The development of this project has been moved to a new repository that
offers an improved structure, additional features, and regular updates.
Please follow the link below to access the new repository:

🔗 [New Repository](https://github.com/rjdemetra/rjd3x13) :
<https://github.com/rjdemetra/rjd3x13>

## Installation


```{r, eval = FALSE}
# Install development version from GitHub
# install.packages("remotes")
remotes::install_github("rjdemetra/rjd3toolkit")
remotes::install_github("rjdemetra/rjd3x13")
```
